---
title: 'RMarkdown:  In Class Assignment'
author: "David Arogunjo"
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```

Reminders:

-   You do not need to memorize Markdown syntax.
-   You are expected to look things up using:
    -   RStudio’s Markdown Help
    -   Online documentation or examples
-   Click Knit as you go to check that your document still renders correctly.
-   Commit at the end, but consider committing as you go as well.

# Part 1: Markdown Practice

**Do not skip reading this instruction** Create a new section at the end of this section named "Your work here". In that section, complete the tasks below:\

# your work Here

-   Make a *subsection* called Wise Words.
-   Put your favorite quote in a block quote.\
    \

## Wise Words

> when someone says you cant do it do it twice and take pictures

-   Add a working, clickable link to a website that provides more information about that quote.

<https://in.pinterest.com/pin/14073817570971580/>

-   Make another *subsection* called "I recommend", and add some information about your favorite author or musician:

## I recommend Dave (British Artist)

> Has a way with words

> The Boy who played the harp (New Album)

-   History
-   175 Months

```         
-   A *subsubheading* with the name of the artist or author;\
-   An example of their writing or lyrics (formatted in a *block of text*);\
-   A *list* of things they have written or performed (remember to use the formatting markup for a list!), with any of the titles/names in bold.
```

# Part 2: Code Chunks

```{r echo=FALSE}
2 + 2
```

Complete the following steps:

-   Knit the document and observe what appears in the output.
-   Change the chunk option echo=TRUE to echo=FALSE.
-   Knit the document again.
-   Finally, write 2–3 sentences answering the following questions:
    -   What changed between the two outputs?

        -   *the equation 2 + 2 was solved when i knitted the document it genarated the answer 4 and when i changed the echo code to false it +Hid the equation and only showed the result.*

    -   Did the calculation still run when the code was hidden?

        -   *yes, the code still ran.*

    -   Why might someone want to hide code in a report?

        -   *it could be to reduce clutter on the document.*

    -   Why might someone want to show code in a report?

        -   *so readers can see the equation.*

# Part 3: A small R-in-markdown preview

## About this document

-   Write 2–3 sentences describing what this document is and what it produces.

    this a markdown document with instructions to for students to learn to use markdown commands and get familiar with its format.

-   Include one value generated by inline R code.

`r 90 + 4`

> To include inline code, use this weird little `r 2+2` pattern, putting the code where I have 2+2 (which is code!) You can use the function `Sys.Date()`, which would be added like this `r Sys.Date()` but you can do something else if you want. (Look at the knit html to see what this does.)

`r Sys.Date()`

# Submitting Instructions

When you are finished:

-   Knit the document so that it produces an html file.
-   Stage, commit, and push:
    -   The updated `.rmd` file
    -   The generated `.html` file
-   Submit the GitHub link to the assignment on Canvas.
